混合效应模型和计量面板数据模型的区别

### 2019-03-25 Panel-and-Mixed-Model.Rmd
修改混合效应模型部分

```{r eval=T,ecol=F,results='markup', cache=F}
library(lme4)
library(lmerTest)
data<-read.csv("./data/pdataquality.csv")
data<-data[which(data$province!="全国"),]
me.nlme<-lmer(gdp~capital+labor+edu+(1|province)+(capital|province)+(edu|province),data=data,REML=TRUE)
knitr::kable(summary(me.nlme)$coefficient, row.names =T, align = "c", caption="混合效应模型固定效应系数",
      digits=7,
      longtable = TRUE, booktabs = TRUE, linesep  = "")
knitr::kable(ranef(me.nlme)$province, row.names =T, align = "c", caption="混合效应模型随机效应系数",
      digits=7,
      longtable = TRUE, booktabs = TRUE, linesep  = "")
```

>>>>

```{r eval=T,ecol=F,results='markup', cache=F}
library(lme4)
library(lmerTest)
data<-read.csv("./data/pdataquality.csv")
data<-data[which(data$province!="全国"),]
me.nlme<-lmer(gdp~capital+labor+edu+(1|province)+(0+capital|province)+(0+edu|province),data=data,REML=TRUE)
knitr::kable(summary(me.nlme)$coefficient, row.names =T, align = "c", caption="混合效应模型固定效应系数",
      digits=7,
      longtable = TRUE, booktabs = TRUE, linesep  = "")
```

```{r eval=T,ecol=F,results='markup', cache=F}
knitr::kable(ranef(me.nlme)$province, row.names =T, align = "c", caption="混合效应模型随机效应系数",
      digits=7,
      longtable = TRUE, booktabs = TRUE, linesep  = "")
```
